---
title: "R Notebook"
output: html_notebook
---

## Packages

[here](https://shirinsplayground.netlify.app/2021/04/goodbadugly_ml/)
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
library(DataExplorer)
library(caret)
```

## Loading functions

```{r}
source("code/functions/color_pallet.R")
```


## Data

```{r, message=FALSE, warning=FALSE, results='hide'}
diabetic_data_initial <- read_csv("data/src/diabetic_data_initial.csv", na = c("?"))
```


## Understand data

```{r}
glimpse(diabetic_data_initial)

introduce(diabetic_data_initial)

plot_missing(
    diabetic_data_initial
)
```
```{r}
plot_missing(
    diabetic_data_initial %>%
    select(-weight, -payer_code, -medical_specialty) %>%
    filter(
        !duplicated(patient_nbr),
        !discharge_disposition_id %in% c(11, 13, 14, 19, 20, 21)
    )
)

# understand levels in medical specialty
table(diabetic_data_initial$medical_specialty, diabetic_data_initial$readmitted)
## adds no value

# other missing with small values
table(diabetic_data_initial$race)
## all missing in race can be assigned to other from a demographic prespective since no other value available to fix issue

# labeled out for formatting purposses
# table(as.factor(diabetic_data_initial$diag_3))
## assign after transformation to majority for all diags
```

## Data processing

```{r}
source("./code/functions/icd9_transform_function.R")
diabetic_data <- diabetic_data_initial %>%
    # drop major missing vars (Medical Specialty is uniform across readmission, adds no value)
    select(-weight, -payer_code, -medical_specialty) %>%
    filter(
        !duplicated(patient_nbr),
        !discharge_disposition_id %in% c(11, 13, 14, 19, 20, 21)
    ) %>%
    # fix missing for variables with minimum threshhold for missing (n < 30%)
    mutate(
        race = as.factor(ifelse(is.na(race), "Other", race)),
        diag_1 = as.factor(diag_mutation(diag_1)),
        diag_2 = as.factor(diag_mutation(diag_2)),
        diag_3 = as.factor(diag_mutation(diag_3)),
        readmitted = ifelse(readmitted == ">30", "NO", readmitted)
    ) %>%
    mutate_if(is.character, as.factor) %>%
    mutate(
        admission_type = case_when(
            admission_type_id == 1 ~ "Emergency",
            admission_type_id == 2 ~ "Urgent",
            admission_type_id == 3 ~ "Elective",
            admission_type_id %in% c(4, 5, 6, 7, 8) ~ "Other"
        ),
        discharge_disposition = case_when(
            discharge_disposition_id == 1 ~ "Discharged to home",
            discharge_disposition_id == 2 ~ "Discharged/transferred to another short term hospital",
            discharge_disposition_id == 3 ~ "Discharged/transferred to SNF",
            discharge_disposition_id == 5 ~ "Discharged/transferred to another type of inpatient care institution",
            discharge_disposition_id == 6 ~ "Discharged/transferred to home with home health service",
            discharge_disposition_id == 22 ~ "Discharged/transferred to another rehab fac",
            T ~ "Other"
        ),
        admission_source = case_when(
            admission_source_id == 1 ~ "Physician Referral",
            admission_source_id == 2 ~ "Clinic Referral",
            admission_source_id == 4 ~ "Transfer from a hospital",
            admission_source_id == 6 ~ "Transfer from another health care facility",
            admission_source_id == 7 ~ "Emergency Room",
            T ~ "Other"
        ),
        number_inpatient = case_when(
            number_inpatient > 5 ~ "Greater than 5 visits",
            number_inpatient == 4 ~ "4",
            number_inpatient == 3 ~ "3",
            number_inpatient == 2 ~ "2",
            number_inpatient == 1 ~ "1",
            number_inpatient == 0 ~ "0"
        ),
        number_outpatient = case_when(
            number_outpatient > 1 ~ "Greater than 1 visit",
            number_outpatient == 1 ~ "1",
            number_outpatient == 0 ~ "0"
        ),
        number_diagnoses = as.factor(ifelse(number_diagnoses > 9, 9, number_diagnoses)),
        A1Cresult = case_when(
            A1Cresult %in% c(">7", ">8") ~ "Diabetic",
            A1Cresult == "None" ~ "No Measurement",
            A1Cresult == "Norm" ~ "Not Diabetic"
        ),
        number_emergency = case_when(
            number_emergency == 0 ~ "0",
            number_emergency == 1 ~ "1",
            number_emergency == 2 ~ "2",
            number_emergency > 2  ~ "More than 2 visits"
        ),
        time_in_hospital = case_when(
            time_in_hospital < 4 ~ "less than 3 days",
            time_in_hospital > 3 ~ "more than 3 days"
        ),
        metformin = case_when(
            metformin %in% c("Down", "Up", "Steady") ~ "Yes",
            metformin == "No" ~ "No"
        ),
        glipizide = case_when(
            glipizide %in% c("Down", "Up", "Steady") ~ "Yes",
            glipizide == "No" ~ "No"
        ),
        glimepiride = case_when(
            glimepiride %in% c("Down", "Up", "Steady") ~ "Yes",
            glimepiride == "No" ~ "No"
        ),
        glyburide = case_when(
            glyburide %in% c("Down", "Up", "Steady") ~ "Yes",
            glyburide == "No" ~ "No"
        ),
        pioglitazone = case_when(
            pioglitazone %in% c("Down", "Up", "Steady") ~ "Yes",
            pioglitazone == "No" ~ "No"
        ),
        rosiglitazone =  case_when(
            rosiglitazone %in% c("Down", "Up", "Steady") ~ "Yes",
            rosiglitazone == "No" ~ "No"
        ),
        num_procedures = as.factor(num_procedures)
    ) %>%
    select(
        -c(admission_type_id, admission_source_id, discharge_disposition_id)
    ) %>%
    filter(gender != "Unknown/Invalid") # removing gender grouping as it has no effect on readmission

```

## Data analysis

### Distribution of Readmissions

```{r}
diabetic_data %>%
    ggplot(aes(x = readmitted, fill = readmitted)) +
    geom_bar(alpha = 0.8) +
    theme(legend.position = "none") +
    labs(x = "Readmissions", 
         y = "count",
        title = "Distribution of Readmissions")
```


### Checking on categorical variables

```{r}
plot_bar(diabetic_data)
```

outcome: 
- drop third gender and check for zero and near zero variance  
- Rule 1: if number of ip admits is > 4, then readmit == High

### Checking on other variables distributions

```{r}
plot_histogram(diabetic_data)
```
Outcome: 
- assign variables as factors as necessary and drop others  

## Model preprocessing

The categorical variables indicate various zero or near zero variances, we need to further explore these to understand which need to be dropped
```{r}
diab_nvz = diabetic_data %>%
    select(-readmitted) %>%
    nearZeroVar(., saveMetrics = TRUE)

drop <- diab_nvz %>%
    dplyr::filter(zeroVar == T | nzv == T) 


diabetic_data_processed <- diabetic_data %>%
    dplyr::select(-one_of(row.names(drop))) %>%
    dplyr::filter(gender != "Unknown/Invalid")

plot_bar(diabetic_data_processed, by = "readmitted")
```


## Modelling

```{r}

```


## Model analysis

## Model production

## Model Scaling
